\documentclass{article}

% For Title modifications
\usepackage{titling} % Gives the \theauthor command

% For Section modifications
\usepackage[center]{titlesec} % allows for the titleformat command

% For Margin modification
\usepackage[margin=1in]{geometry} % allows for changing the shape of a document

% https://tex.stackexchange.com/questions/823/remove-ugly-borders-around-clickable-cross-references-and-hyperlinks
% Hyper Link modifications
\usepackage[hidelinks]{hyperref}
\hypersetup{
	colorlinks = true, % Colours links instead of ugly boxes
	urlcolor   = blue  % Colour for external hyperlinks
}

% Title modification
\renewcommand{\maketitle}{
\begin{center}
{\Large\bfseries
\theauthor}

\vspace{0.75em}

\href{mailto://defrann8208@outlook.com}{defrann8208@outlook.com} ---
\url{https://nicholasdefranco.xyz/}

\vspace{0.25em}

\end{center}
}

% Section modification
\titleformat{\section}
{\bfseries\Large}
{}
{0em}
{}[\titlerule]

% Subsection modification
\titleformat{\subsection}
{\center\bfseries}
{}
{0em}
{\underline}[\vspace{0.5em}]

% Subsection modification
\titleformat{\subsubsection}[runin]
{\center\bfseries}
{}
{0em}
{}[\hspace{0.25em}---\vspace{1.0em}]

% Item modification
\renewcommand{\labelitemi}{-}

\begin{document}

\title{R\'esum\'e}
\author{Nicholas Defranco}

\maketitle

% https://tex.stackexchange.com/questions/7355/how-to-suppress-page-number#7357
\pagenumbering{gobble}

\section{Relevant Skills}

\subsection{Reliability}

\begin{itemize}

\item Demonstrated the ability to work with others effectively in school and
	other activities.

\item Able to have assignments/projects completed on time.

\item Proven to stay on task for in class work at school.

\item Able to listen to detailed instructions at school and work.

\end{itemize}

\subsection{Technical skills}

\begin{itemize}

\item Familiar with the Linux operating system.

\item Familiar with C and C++ programming for application development.

\item Experience with database design and programming in Oracle SQL (SQL and
	PL/SQL).

\item Strong Understanding of the How to Design Programs recipe

\end{itemize}

\section{Experience}

\subsection{Portfolio}

\subsubsection{Personal Projects}

\url{https://github.com/NicholasDefranco}

\section{Education}

\subsection{Seneca College}

\subsubsection{CPD}

Computer programming --- Fall 2018 - Summer 2020

Courses: Linux, C/C++ Programming, Database Design and Programming
(With Oracle), Web Development using HTML, CSS, and JavaScript.

\subsubsection{Part-Time}

Web programming --- Fall 2020 - present

Course: PHP web development

\end{document}
